Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
typos, punctuations, language, conciseness, clarity

In this example, we exercise the framework on a real-world testbed
located in a laboratory.
%
In particular,
we want to avoid situations where too many people are too close to each other in the same room for safety reasons.
%
To do so,
we equip each person with a wearable device that can detect the distance from other similar devices via Bluetooth.
%
For the sake of simplicity,
we relied on smartphones to emulate wearables,
and we used
% \meta{
%     NICOLAS please write here (within meta, so that it remains blue)
%     what you used to measure the signal strenght and estimate the distance.
%     Even formulas, calibration procedures, and stuff
% }
%
%\meta{
    the Bluetooth \ac{rssi} to estimate the distance $d$ between devices as:
    $$d=10^{\frac{R_{ref} - R}{10 \cdot n}}$$
    where $R_{ref}$ is the \ac{rssi} reference value at 1 meter,
%    (calibrated in a test environment by measuring it with two smartphones),
    R is the currently measured \ac{rssi},
    and $n$ is the path loss exponent,
    a parameter indicating the rate at which the \ac{rssi} decreases with distance.
    %
    $R_{ref}$ and $n$ are environment-sensitive parameters that require calibration;
    we set up a test with two smartphones and measured,
    for our setup,
    $R_{ref}\qty{-60}{\decibelmeter}$ and $n=\qty{2.0}{\decibel}$.
%    Since the definition of $A'$ and $n$ is not trivial,
%    and depends on the environment in which the system is deployed,
%    we have calibrated the system in a test environment by measuring the RSSI signal
%    at 1 meter using two smartphones.
%    %
%    The following values emerged from the calibration phase:
%    $A=\qty{-60}{\decibelmeter}$ and $n = \qty{2.0}{\decibel}$.
%}
%
We used a monitor to issue the warning
by setting its colour from green to red depending on the average distance among people:
the shorter the distance, the redder the tone.
%
\Cref{fig:crowd-alert} shows a representation of the scenario.
%
\begin{figure}
    \centering
    \includegraphics[width=.9\columnwidth]{figures/crow-laboratory-demo.drawio.pdf}
    \caption{
        Representation of the scenario described in \Cref{sec:small-scale-crowd-alert}.
        graph dots represent wearables,
        and arcs lenghts represent the distance between them.
        %
        The rectangle at the bottom represents the monitor.
        %
        The closer the wearables are, the higher is the alert level
        (reddish tones).
    }
    \label{fig:crowd-alert}
\end{figure}

>>>>

In this example, we exercise the framework on a real-world testbed
located in a laboratory.
%
In particular,
we want to avoid situations where too many people are too close to each other in the same room for safety reasons.
%
To do so,
we equip each person with a wearable device that can detect the distance from other similar devices via Bluetooth.
%
For the sake of simplicity,
we relied on smartphones to emulate wearables,
and we used
% \meta{
%     NICOLAS please write here (within meta, so that it remains blue)
%     what you used to measure the signal strenght and estimate the distance.
%     Even formulas, calibration procedures, and stuff
% }
%
%\meta{
    the Bluetooth \ac{rssi} to estimate the distance $d$ between devices as:
    $$d=10^{\frac{R_{ref} - R}{10 \cdot n}}$$
    where $R_{ref}$ is the \ac{rssi} reference value at 1 meter,
%    (calibrated in a test environment by measuring it with two smartphones),
    R is the currently measured \ac{rssi},
    and $n$ is the path loss exponent,
    a parameter indicating the rate at which the \ac{rssi} decreases with distance.
    %
    $R_{ref}$ and $n$ are environment-sensitive parameters that require calibration;
    we set up a test with two smartphones and measured,
    for our setup,
    $R_{ref}\qty{-60}{\decibelmeter}$ and $n=\qty{2.0}{\decibel}$.
%    Since the definition of $A'$ and $n$ is not trivial,
%    and depends on the environment in which the system is deployed,
%    we have calibrated the system in a test environment by measuring the RSSI signal
%    at 1 meter using two smartphones.
%    %
%    The following values emerged from the calibration phase:
%    $A=\qty{-60}{\decibelmeter}$ and $n = \qty{2.0}{\decibel}$.
%}
%
We used a monitor to issue the warning
by setting its colour from green to red depending on the average distance among people:
the shorter the distance, the redder the tone.
%
\Cref{fig:crowd-alert} shows a representation of the scenario.
%
\begin{figure}
    \centering
    \includegraphics[width=.9\columnwidth]{figures/crow-laboratory-demo.drawio.pdf}
    \caption{
        Representation of the scenario described in \Cref{sec:small-scale-crowd-alert}.
        graph dots represent wearables,
        and arc lengths represent the distance between them.
        %
        The rectangle at the bottom represents the monitor.
        %
        The closer the wearables are, the higher the alert level
        (reddish tones).
    }
    \label{fig:crowd-alert}
\end{figure}
